\documentclass[12pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\hypersetup{
	colorlinks=true,
}
\pagestyle{fancy}
\fancyhf{}

\fancyhead[L]{\huge{Thomas Nguyen}}
\fancyhead[R]{(405) 558-1550}
\fancyhead[C]{thomas.t.nguyen-5@ou.edu}
\begin{document}

\section*{Education}
\textbf{University of Oklahoma}, Norman, OK \\
Bachelor of Science in Computer Science, May 2024 
% \\ Cumulative Grade Point Average: 4.0

\section*{Leadership / Involvement}
AT\&T Summer Bridge Program, Summer 2020 
\begin{itemize}
\item Participant: Learned through hands-on experience: the engineering design process, collaboration,  and professionalism.
\end{itemize}

OU Diversity and Inclusion Program, 2020 - Present 
\begin{itemize}
\item Member: Experienced the importance of diversity, equity, and inclusion in engineering through seminars and group activitties.
\end{itemize}

OU ME\textasciicircum{}2 Program, 2020 - Present 
\begin{itemize}
\item Mentee: Cultivated relationships with upperclassmen engineers to learn about future possibilities and engineering perspectives.
\end{itemize}

Youth Leadership Exchange: Leadership Skills Class XXV, 2019 
\begin{itemize}
\item Student: Learned leadership traits through collaborative activities with an emphasis on the Oklahoma City community.
\end{itemize}

\begin{multicols}{2}
\section*{Relevant Classwork}
Introduction to Computer Programming  \\
Programming Structures and Abstractions \\
Diversity and Inclusion Orientation \\
Linear Algebra

\section*{Awards / Honors}
AP Scholar with Honor, 2020 \\
Oklahoma Academic Scholar, 2020-Present \\
Patel Math and Sciences Scholar, 2020-2021 \\
Maples Family Scholar, 2020-2021 
\end{multicols}

%\section{Skills}
%Fluent in Vietnamese \\
%- Native Speaker
%
%Conversational in Spanish \\ 
%- AP Spanish Language and Culture: 3 \\
%- IB Spanish B SL: 5

\section*{Projects}
\href{https://github.com/tttnguyen729/ChessProject}{Chess Project: Developed a program in Java that reads a PGN file and isolates king moves made by either player. Learned the principles of abstraction and implementation of ArrayLists.}

\href{https://github.com/tttnguyen729/lichessRatingParser}{Hacklahoma 2021: Developed a shell script that takes a Lichess username and outputs their chess ratings for convenience}

Rude Goldberg Machine: Worked in a small group to design and build a balloon-popping contraption. Learned collaboration, project management, and the engineering design process. August 2020.

\href{https://github.com/tttnguyen729/ee}{The Application of a Taylor Series Approximation for \(\pi\) in a Related Rates Problem using a Solid of Revolution: How well can Taylor series approximations for \(\pi\) be applied in rates of change of cyclical objects?} Under the advisement of Carson Moon: \href{mailto:cmoon@okcps.org}{cmoon@okcps.org}, May 2020 

%\section*{Advanced Coursework}
%\begin{multicols}{3}
%AP Calculus BC \\
%AP US History \\
%IB Chemistry HL \\
%IB Biology HL \\
%IB English Lang and Lit HL \\
%IB Spanish SL \\
%IB Mathematics SL \\
%IB History SL \\
%IB Theory of Knowledge
%\end{multicols}

%\section{Skills}
%\section{Work Experience}
\end{document}
